\documentclass[titlepage]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{tikz}

\begin{document} 
\section*{200 Level Problems}
\subsection*{CUPCAKES}The $<\textsf{ColgateCoders}>$ are organizing \textbf{Colgate Cupcakes and Coding 2020}. Megan has placed an order of $N$ cupcakes. Brittney's task, as the cupcake incharge, is to place the cupcakes into bags each of capacity $C$. Each bag should have exactly $C$ cupcakes. If there are leftover cupcakes that do not fill, she gets to eat them. Brittney really likes \textsl{Flour \& Salt} cupcakes. Help her find the ideal bag capacity that will maximize the number of cupcakes she gets to eat.
\subsubsection*{Input Format}
\begin{enumerate}
\item The first line contains an integer $1\le T \le 500$.
\item The following $T$ lines contain integers $N_1, N_2, \dots, N_T$ where each integer is less than 100,000. 
\end{enumerate}
\subsubsection*{Output Format}
\hspace{10mm}For each $N_i$, print out the bag capacity $C$ that maximizes the number of cupcakes Brittney gets to eat. Each capacity should be on its own line. For each $N_i$, the corresponding capacity $C_i$ should not exceed $N_i$.
\subsubsection*{Sample Input}
3 \newline
3 \newline
5 \newline
2
\subsubsection*{Expected Output}
2 \newline
3 \newline
2

\subsubsection*{Explanation} 
There are $3$ Test cases here ($T = 3$). For the first case, if there are $3$ cupcakes and a bag of capacity $2$, Brittney will fill up the first bag with $2$ cupcakes, but the remaining cupcake is insufficient to fill up the rest, so she gets to eat it. This is the largest number of cupcakes she gets to keep since the other choices are bags of capacity $1$ or $3$, which wouldn't allow her to keep any. Similarly, for an order of $5$ cupcakes, using bags of capaciy $3$ yields $2$ leftover cupcakes. Note for the last case, there are $2$ cupcakes, so the two options for bag capacity are $1$ and $2$, both of which leave Brittney with no cupcakes. 
\newline \newline
When there are multiple bag capacities that allow the maximum number of leftover cupcakes, choose the largest number. 

\subsubsection*{For 25 points...}
Use \textbf{test1.in} as your test input, your output should match \textbf{test1.out}.
\newpage



\end{document}